---
title: "CAR EVALUATION"
author: "Shreya PS"
date: "2024/01/28"
output:
  word_document: default
  html_document: default
theme: darkly
---
#loading the dataset
```{r}
df<-read.csv("C:\\Users\\Shreya\\OneDrive\\Desktop\\cardata.csv")
```
#printing the summary of the dataframe
```{r}
summary(df)
```
#checking the structure of the dataframe
```{r}
str(df)
```
#displaying the first few rows of the dataframe
```{r}
head(df)
```
#accessing the column in a dataframe
```{r}
df$DOORS
```
#getting the names of all columns in the dataset
```{r}
names(df)
```
#checking the datatype of a column
```{r}
class(df$SAFETY)
```
#creating a dataset of data frame where Number of Persons is less than 4
```{r echo=TRUE}
subset_df <- df[df$PERSONS < 4, ]
subset_df
```
#removing the "DOORS" column
```{r}
df$DOORS <- NULL
summary(df)
```
#renaming the "lug_boot" column to "bootspace"
```{r}
names(df)[names(df) == "LUG_BOOT"] <- "BOOTSPACE"
summary(df)
```
#converting data type
```{r}
as.numeric(df$BUYING)
```
#displaying frequency counts for "buying"
```{r}
table(df$BUYING)
```
#calculating average 
```{r}
library(dplyr)

avg_safety_by_VALUES <- df %>%
  group_by(VALUES) %>%
  summarise(Avg_Safety = mean(as.numeric(factor(SAFETY, levels = c("low", "med", "high")))))
avg_safety_by_VALUES


```








